\documentclass[t,12pt]{beamer}

\usepackage{pgfpages}
%\setbeameroption{show notes on second screen=left}

\usepackage{graphicx}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}

\usetheme{metropolis}
\title{SCRUM Club}
\subtitle{Software and Tools for Scientific Computing\\ and Research @ UM Club}
\date{\today}
\author{Wolfgang Viechtbauer\\Ozan \c{C}{\i}nar\\Sander van Kuijk}
\institute{Maastricht University}

\graphicspath{{images/}}

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[standout]

   The First Rule of SCRUM Club:\\
   \vspace{1ex}
   \visible<2->{You do talk about SCRUM Club.}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[standout]

   The Second Rule of SCRUM Club:\\
   \vspace{1ex}
   You DO talk about SCRUM Club.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Rules 3-8}

\begin{description}
\item[3rd rule] Someone yells stop, goes limp, taps out, the presentation is over.
\item[4th rule] Only at most two presenters for a presentation.
\item[5th rule] One presentation at a time, fellas (and gals).
\item[6th rule] No shirts, no shoes = no presentation.
\item[7th rule] SCRUM Club will go on as long as it has to.
\item[8th rule] If this is your first night at SCRUM Club, you must have fun.
\end{description}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Okay, so what is this all about?}

\begin{itemize}
   \item a group to explore and learn about software and tools for scientific computing and research
   \item we start with R, but there are many other \href{https://wviechtb.github.io/scrum-club/topics.html}{topics}
   \item open to students at all levels, post-docs, staff, faculty members, researchers, ...
   \item no prerequisites for joining
   \item do not have to be affiliated with UM
   \item no need to sign up or register
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Logistics}

\begin{itemize}
   \item meetings every two weeks
   \item Wednesdays from 16:30 to 18:00
   \item \href{https://wviechtb.github.io/scrum-club/schedule.html}{schedule} and \href{https://wviechtb.github.io/scrum-club/materials/materials.html}{materials} on website
   \item room:
   \begin{itemize}
      \item wanted something with free-standing chairs/desks and some space outside to hang out ...
      \item first three meetings in room H1.319 at UNS50
      \item then in \href{http://www.mumcplattegrond.nl/\#map/d99_d26}{Greepzaal} at the AZM
   \end{itemize}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Our Vision}

\begin{itemize}
   \item this is not a `course', it's a user-driven club
   \item we can teach some things, but ultimately we need members (and guest speakers) to give presentations
   \item 45-60 minutes for presentation(s), the rest is `free hacking' and hangout time
   \item don't have to be an expert to present something
   \item can form `interest groups' to learn together
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Links}

\begin{itemize}
   \item website: {\footnotesize \url{https://wviechtb.github.io/scrum-club/}}
   \begin{itemize}
      \item keep an eye on the `blog' for announcements
      \item want to be listed on the members list? make a \href{https://help.github.com/articles/about-pull-requests/}{pull request} on GitHub or send your info to Wolfgang\footnote{wolfgang.viechtbauer at maastrichtuniversity.nl}, Ozan\footnote{ozan.cinar at maastrichtuniversity.nl}, or Sander\footnote{sander.van.kuijk at mumc.nl} via email
   \end{itemize}
   \item Slack channel: {\footnotesize \url{https://scrum-club.slack.com/}}
\end{itemize}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
